D-Hammer: Practical Proof Automation of Dirac Notation Equations

### 2025-01-28 01intro_preliminary.tex

Labelled Dirac notation is also commonly used to express assertions
about quantum programs. Specifically, many quantum Hoare logics use
labelled Dirac notation to express program assertions, including
pre-conditions and post-conditions. These logics also use implicitly
equational reasoning between labelled Dirac expressions, to glue
applications of proof rules---similar to the use of the rule of
consequence in the setting of classical program. Therefore, it is
essential for the verification of quantum programs to have automated
means of proving equality of two complex expressions based on labelled
Dirac notation.

>>>>

Labelled Dirac notation is also commonly used to express assertions
about quantum programs. Specifically, many quantum Hoare logics use
labelled Dirac notation to express program assertions, including
pre-conditions and post-conditions~\cite{TODO}. These logics also use
implicitly equational reasoning between labelled Dirac expressions, to
glue applications of proof rules---similar to the use of the rule of
consequence in the setting of classical program. Therefore, it is
essential for the verification of quantum programs to have automated
means of proving equality of two complex expressions based on labelled
Dirac notation.
